% !TeX spellcheck = en_US
\cvsection{Experience}
\begin{cventries}

\cventry
    {Tech Lead Software Engineer} % 
    {The Hut Group} % Institution     	
    {} % Location
    {2019 - 2022} % Date(s)
    {
    \begin{cvitems}
        \item{Part of a medium sized team, developing the THG proprietary warehouse management system, developing, maintaining and improving and optimisying order picking/packing, parcel sortation and dispatch. Worked to decouple a monolith of over 50 applications, initially to a set of 3 warehouses which later grew to 12. Using a SCRUM process to build a platform, using an Event-Driven Architecture to deliver configurable solutions for allocating and batching orders.}
        \item{Identify manual processes and make a priority to improve them. Propose and deliver work to automate processes to remove ownership of manual tasks and save development time. Analyse performance and optimise one of the management workflows by eliminating redundant data and processes to improve scalability, responsiveness and overall performance of the application to align with the peak period needs.}
        \item{Started a greenfield project within the company with a medium-sized team. Built new processes from the ground up to accommodate a new set of workflow and administrative management tools, communicating with the existing system to allow product personalisation. We integrated with third-party software and hardware to allow automated bottle engraving, artwork composition, printing and product assembly.}
        \item{Increase involvement in issue and incident management and further develop as an Engineering Lead by identifying personal areas to improve, such as stakeholder management and actively seeking regular feedback on my work.}
        \item{Closely mentor and lead a medium sized team as well as contribute in terms of support and coordination with the larger team.}
        \item{Continue to be a point of reliance and support for new and older team members.}
        \item{Made use of new technologies and mentored a group of new members, as well as started covering scope, documentation of system design and implementation of features. Being a new platform, the applications require a high level of attention with a limited pool of people available for support, close contact with the operatives, as well as with upstream teams and a higher stakeholders involvement.}
        \item{Get more and more involved in incidents and start participating in the on call shift rotation, being the point of contact to resolve any major incidents arising at any point in the shift.}
  \end{cvitems}
  }

\end{cventries}
