\cventry
{Software Engineer} %
{The Hut Group} % Institution
{Manchester, UK} % Location
{2019 - 2023} % Date(s)
{\begin{cvitems}
     \item{Part of a medium-sized team, developing the company's proprietary Warehouse Management System
     capable of fulfilling orders from hundreds of websites with stock for millions of products. Fulfiling
     orders for 15 warehouses split between four continents ensuring seamless operation for over a million daily orders
     a day during peak periods. The intricate ballet of storing, picking, packing, sorting and shipping was powered by
     over 50 microservices. Adopting the SCRUM methodology, we steadily advanced this platform, crafting highly
     configurable solutions within an Event-Driven Architecture, we have delivered projects of immense value, worth
     millions of pounds.}
     \item{I embarked on my journey as a Graduate Software Engineer, advancing to the role of Software Engineer and
     embracing the path of leadership development. Early in my tenure, I took on the mantle of responsibility,
     participating in on-call shift rotations for over two years, serving as the pivotal point of contact to address and
     resolve major incidents with unwavering resolve.}
     \item{Analysed system performance, proposed and delivered work to automate and optimise manual
     processes or improve scalability and responsiveness to align with peak period needs. Made use of
     new technologies, mentored a group of new members and started covering scope, documentation of system
     design and implementation of new features.}
     \item{Developed an adaptive skillset for accurately assessing and quickly responding to high-impact events.
     Leveraged Python scripting to diagnose issues, implement fixes, and provide temporary solutions during emergencies.}
\end{cvitems}}